Query Optimization for Dynamic Imputation

### 2017-06-30 paper/algorithm.tex
fig 4: fix to avoid dirty set issue

\begin{figure}
  \begin{align*}
    \llbracket Q[T] \rrbracket &= \begin{cases}
      P & (T, P) \in Q \\
      \emptyset & \text{otherwise} \\
    \end{cases} \\
    \llbracket Q[T] \lhd p \rrbracket &= \begin{aligned} Q \cup \{(T,\ P') \} \end{aligned}\\
    \text{ where }\ P' &= \left\{q ~\Bigg|~ \begin{aligned}
        q \in \llbracket Q[T] \rrbracket \cup \{p\}, \\
        \textsc{Dirty}(q) = \textsc{Dirty}(p),\\
        \forall q' \in \llbracket Q[T] \rrbracket.  \doms{q} {q'} 
      \end{aligned}
    \right\}
  \end{align*}
  \caption{Semantics of a plan cache $Q$, where $T$ is a set of tables and $p$ is a query plan}
  \label{fig:semantics-plan-cache}
\end{figure}

>>>>

\begin{figure}
  \cameraready{
  \begin{align*}
    \llbracket Q[T] \rrbracket &= \begin{cases}
      P & (T, P) \in Q \\
      \emptyset & \text{otherwise} \\
    \end{cases} \\
    \llbracket Q[T] \lhd p \rrbracket &= \begin{aligned} Q \cup \{(T,\ P') \} \end{aligned}\\
    \text{ where }\\ 
    S = \llbracket Q[T] \rrbracket \cup \{p\}\\
    \text{ in }
    P' &= \left\{q ~\Bigg|~ \begin{aligned}
              q \in S,\\
              \textsc{Dirty}(q) = \textsc{Dirty}(p) \implies\\
              \not \exists q' \in S.\doms{q'}{q}
              \end{aligned}
            \right\}
  \end{align*}
  \caption{Semantics of a plan cache $Q$, where $T$ is a set of tables and $p$ is a query plan. \cameraready{When extending with a new plan $p$, the cache guarantees
  no dominated plans with the same dirty set are kept.}}
  \label{fig:semantics-plan-cache}
  }
\end{figure}
